Supplementary Materials: The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-07-13 analysis/analysis.Rmd
Fixed sup mat legends

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv") 
both_plts + plot_annotation(title = 'Odd harmonic data from parietal electrodes')

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts + plot_annotation(title = 'Even harmonic data from occipital electrodes')
```

>>>>

both_plts <- p1 + p2 + plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')
both_plts + plot_annotation(title = 'Odd harmonic data from parietal electrodes')

@@

both_plts <- p1 + p2 + plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')
both_plts + plot_annotation(title = 'Even harmonic data from occipital electrodes')
```
